INTELLIGENT SYSTEMS

### 2021-03-29 paper_3.tex
finish 3.2.3

\subsubsection{Image Compression Based on Deep Learning}

>>>>

\subsubsection{Image Compression Based on Deep Learning}
Deep learning was used for lossy and loseless compressions achieving good 
performance. There have been some methods that have prevailed over others. 
However, all of these methods ignore compatibility with various image codecs, 
thus limiting their use in some existing systems. The proposed framework 
solves this problem by operating with different image codecs, also taking into 
account the compression performance.
